Through the eyes of the teacher - Multimodal exploration of expertise differences

### 2024-10-25 02_paper/02_study/01_fitbit_paper/R_scripts/analysis_190423.Rmd

lm_plot_phases

ggsave(filename = "plots/test.pdf")
```

@@

table_data <- 
  df_regression %>% 
 # mutate(time = time * 60) %>% 
  split(.$Phase) %>% 
  map(~ lmerTest::lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[1],
               intercept_sd = VarCorr(.) %>% as_tibble(.) %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[2],
               slope_sd = VarCorr(.) %>% as_tibble(.) %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = intercept,
            `SD(Intercept)` = intercept_sd$sdcor,
            `p-Value (Intercept)` = intercept_p,
            `Mean(Slope)` = slope, 
            `SD(Slope)` = slope_sd$sdcor,
            `p-Value (Slope)` = slope_p, 
            )

@@

model_pre <- 
  df_regression %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .)
model_teach <- 
  df_regression %>% 
  filter(Phase == "Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_post <- 
  df_regression %>% 
  filter(Phase == "Post Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_int <- 
  df_regression %>% 
  filter(Phase == "Interview Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_end <- 
  df_regression %>% 
  filter(Phase == "End Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))

tib_pre <-

```{r}
df_regression <- 
  main %>% 
  filter(time_span != "overall") %>%
  dplyr::select("ID", "time_span","time","heart_rate_std") %>% 
  distinct() %>% 
  mutate(time = time / 100) %>% 
  mutate(ID = as_factor(ID),
         Phase = factor(time_span,
                           levels = c("preparation","teaching","post","interview","end"),
                            labels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           )
         )

fix_models <-
  df_regression %>% 
  split(.$Phase) %>% 
  map(~ lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .
       )
      ) %>% 
    map(~ coef(.) %>%
          tibble::as_tibble(.,
                            rownames = "name") %>%
          transmute(type = if_else(str_detect(name,
                                              ":"),
                                   true = "slope",
                                   false = "intercept"),
                    id = str_remove_all(name,
                                        "[^[:digit:]]"),
                    value = value
                    ),

    ) %>% 
    bind_rows(.id = "Phase") %>% 
    pivot_wider(names_from = type,
                values_from = value
                )
p.values_slope <- 
  fix_models %>% 
  split(.$Phase) %>% 
  map(~ t.test(x = .$slope,
             mu = 0)$p.value
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_slope")

p.values_intercept <- 
  fix_models %>% 
  split(.$Phase) %>% 
  map(~ t.test(x = .$intercept,
             mu = 0)$p.value
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  pivot_longer(cols = everything(),
               names_to = "Phase",
               values_to = "p.value_intercept")

sd_mean <- 
  fix_models %>% 
  group_by(Phase) %>% 
  summarize(mean_slope = mean(slope),
            sd_slope = sd(slope),
            mean_intercept = mean(intercept),
            sd_intercept = sd(intercept))

model_teach_fix <- 
  df_regression %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  mutate(time = time / 60) %>% 
  lm(formula = heart_rate_std ~ 0 + ID + time:ID,
       data = .)

table_data <- 
  right_join(x = sd_mean,
             y = p.values_intercept,
             by = "Phase") %>% 
  right_join(x = .,
             y = p.values_slope,
             by = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = mean_intercept,
            `SD(Intercept)` = sd_intercept,
            `p-Value (Intercept)` = p.value_intercept,
            `Mean(Slope)` = mean_slope, 
            `SD(Slope)` = sd_slope,
            `p-Value (Slope)` = p.value_slope, 
            ) %>% 
  arrange(Phase)

model_teach_fix %>% 
  coef(.) %>% 
  tibble::as_tibble(.,
                    rownames = "name"
                    ) %>% 
  mutate(type = if_else(str_detect(name,
                                   ":"),
                        true = "slope",
                        false = "intercept"
                        )
         ) %>% 
  filter(type == "slope") %$% 
  t.test(x = value,
         mu = 0) -> test

test$

model_pre <- 
  df_regression %>% 
  filter(Phase == "Pre Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .)
model_teach <- 
  df_regression %>% 
  filter(Phase == "Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_post <- 
  df_regression %>% 
  filter(Phase == "Post Teaching Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_int <- 
  df_regression %>% 
  filter(Phase == "Interview Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))
model_end <- 
  df_regression %>% 
  filter(Phase == "End Phase") %>% 
  lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID))

summary(model_teach_fix)

>>>>

plot_overall
```

@@

table_data <- 
  df_regression %>% 
#  mutate(time = time * 60) %>% 
  split(.$Phase) %>% 
  map(~ lmerTest::lmer(formula = heart_rate_std ~ 1 + time + (1 + time | ID),
       data = .
       )
      ) %>%
  map(~ tibble(time_span = names(.),
               intercept = fixef(.)[1],
               intercept_sd = VarCorr(.) %>% as_tibble() %>% .[1,5],
               intercept_p = coef(summary(.))[1, 5],
               slope = fixef(.)[2],
               slope_sd = VarCorr(.) %>% as_tibble() %>% .[2,5],
               slope_p = coef(summary(.))[2, 5]
               )
      ) %>% 
  bind_rows(.id = "Phase") %>% 
  transmute(Phase = factor(Phase,
                           levels = c("Pre Teaching Phase","Teaching Phase","Post Teaching Phase","Interview Phase","End Phase")
                           ),
            n = NA,
            `Mean(Intercept)` = round(intercept, digits = 3),
            `SD(Intercept)` = round(intercept_sd$sdcor, digits = 3),
            `p-Value (Intercept)` = round(intercept_p, digits = 3),
            `Mean(Slope)` = round(slope, digits = 3),
            `SD(Slope)` = round(slope_sd$sdcor, digits = 3),
            `p-Value (Slope)` = round(slope_p, digits = 3)
            )

@@

### 2024-10-25 02_paper/02_study/01_fitbit_paper/R_scripts/fitbit_paper.tex

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
  pdfauthor={Mandy Klatt1, Peer Keßler1, Gregor Kachel1,2, Christin Lotz1, \& Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={heart rate; photoplethysmography; wearable electronic device; teaching},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\begin{tabular}{ll}
\toprule
Variable & \multicolumn{1}{c}{values}\\
\midrule
N & 76.00\\
Gender female in percent & 63.16\\
M Age in years & 30.26\\
SD Age in years & 10.52\\
Min Age in years & 19.00\\
Max Age in years & 59.00\\
M Teaching Experience in years & 5.17\\
SD Teaching Experience in years & 9.12\\
Min Teaching Experience in years & 0.00\\
Max Teaching Experience in years & 37.00\\
\bottomrule
\end{tabular}

@@

The sample consisted in total of \emph{N} = 76 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 76 subjects.

The subjects (48 women; 63.16 \%) had a mean age of 30.30 years (\emph{SD} = 10.50; range: 19-59) and an average teaching experience of 5.17 years (\emph{SD} = 9.12; range: 0-37).

15.79\% of the subjects were (studying to become) teachers for primary school, 71.05\% were (studying to become) teachers for secondary school and 10.53\% were (studying to become) teachers for special education needs.

@@

We used R (Version 4.2.2; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{cowplot} (Version 1.1.1; Wilke, 2020), \emph{DescTools} (Version 0.99.48; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.2; Wickham, 2021), \emph{ggplot2} (Version 3.3.6; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{imputeTS} (Version 3.3; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.2.0; Firke, 2021), \emph{jtools} (Version 2.2.1; Long, 2022), \emph{lm.beta} (Version 1.7.2; Behrendt, 2022), \emph{lme4} (Version 1.1.31; Bates, Mächler, Bolker, \& Walker, 2015), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{MASS} (Version 7.3.58.1; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.7; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.1.9001; Aust \& Barth, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.3.3; Revelle, 2022), \emph{purrr} (Version 0.3.5; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.1; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.1; Kassambara, 2021), \emph{rticles} (Version 0.25; Allaire et al., 2023), \emph{stringr} (Version 1.4.1; Wickham, 2019), \emph{tibble} (Version 3.1.8; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.1; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.2; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), and \emph{xfun} (Version 0.38; Xie, 2022) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 90.40 bpm with a standard deviation of 15.82 and a range from 51 to 164 bpm.

@@

@@

@@

@@

@@

@@

@@

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
Wilke, C. O. (2020). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}

@@

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math} % this also loads fontspec
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else
  % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\ifLuaTeX
\usepackage[bidi=basic]{babel}
\else
\usepackage[bidi=default]{babel}
\fi
\babelprovide[main,import]{english}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same}
\hypersetup{
  pdftitle={New approaches to teachers' experience of stress: Do heart rate measurements with fitness trackers provide an efficient, inexpensive, and robust measurement method?},
  pdfauthor={Mandy Klatt1, Peer Keßler1, Gregor Kachel1,2, Christin Lotz1, \& Anne Deiglmayr1},
  pdflang={en-EN},
  pdfkeywords={heart rate; photoplethysmography; wearable electronic device; teaching},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}

@@

\begin{tabular}{ll}
\toprule
Variable & \multicolumn{1}{c}{values}\\
\midrule
N & 81.00\\
Gender female in percent & 64.20\\
M Age in years & 30.95\\
SD Age in years & 10.87\\
Min Age in years & 19.00\\
Max Age in years & 60.00\\
M Teaching Experience in years & 5.64\\
SD Teaching Experience in years & 9.46\\
Min Teaching Experience in years & 0.00\\
Max Teaching Experience in years & 37.00\\
\bottomrule
\end{tabular}

@@

The sample consisted in total of \emph{N} = 81 pre- and in-service teachers. The subjects were recruited from the Leipzig University or from German schools in Saxony via personal contact, e-mail lists and flyers. Data of two participants were excluded from the analyses due to insufficient data quality, yielding data from \emph{N} = 81 subjects.

The subjects (52 women; 64.20 \%) had a mean age of 31 years (\emph{SD} = 10.90; range: 19-60) and an average teaching experience of 5.64 years (\emph{SD} = 9.46; range: 0-37).

14.81\% of the subjects were (studying to become) teachers for primary school, 70.37\% were (studying to become) teachers for secondary school and 9.88\% were (studying to become) teachers for special education needs.

@@

We used R (Version 4.1.3; R Core Team, 2022) and the R-packages \emph{broom} (Version 1.0.1; Robinson, Hayes, \& Couch, 2022), \emph{corrplot2021} (Wei \& Simko, 2021), \emph{cowplot} (Version 1.1.1; Wilke, 2020a), \emph{DescTools} (Version 0.99.45; Andri et mult. al., 2022), \emph{dplyr} (Version 1.0.10; Wickham, François, Henry, \& Müller, 2022), \emph{forcats} (Version 0.5.1; Wickham, 2021), \emph{ggplot2} (Version 3.3.5; Wickham, 2016), \emph{ggpubr} (Version 0.4.0; Kassambara, 2020), \emph{ggthemes} (Version 4.2.4; Arnold, 2021), \emph{gridExtra} (Version 2.3; Auguie, 2017), \emph{gridtext} (Version 0.1.4; Wilke, 2020b), \emph{Hmisc} (Version 5.0.1; Harrell Jr, 2023), \emph{imputeTS} (Version 3.2; Moritz \& Bartz-Beielstein, 2017), \emph{janitor} (Version 2.1.0; Firke, 2021), \emph{jtools} (Version 2.2.0; Long, 2022), \emph{lm.beta} (Version 1.6.2; Behrendt, 2022), \emph{lme4} (Version 1.1.30; Bates, Mächler, Bolker, \& Walker, 2015), \emph{lmerTest} (Version 3.1.3; Kuznetsova, Brockhoff, \& Christensen, 2017), \emph{ltm} (Version 1.2.0; Rizopoulos, 2006), \emph{lubridate} (Version 1.8.0; Grolemund \& Wickham, 2011), \emph{magrittr} (Version 2.0.3; Bache \& Wickham, 2022), \emph{MASS} (Version 7.3.55; Venables \& Ripley, 2002), \emph{Matrix} (Version 1.5.1; Bates, Maechler, \& Jagan, 2022), \emph{msm} (Version 1.6.9; Jackson, 2011), \emph{needs} (Version 0.0.3; Katz, 2016), \emph{papaja} (Version 0.1.0.9999; Aust \& Barth, 2020), \emph{PerformanceAnalytics} (Version 2.0.4; Peterson \& Carl, 2020), \emph{polycor} (Version 0.8.1; Fox, 2022), \emph{ppcor} (Version 1.1; Kim, 2015), \emph{psych} (Version 2.2.9; Revelle, 2022), \emph{purrr} (Version 0.3.4; Henry \& Wickham, 2020), \emph{readr} (Version 2.1.3; Wickham, Hester, \& Bryan, 2022), \emph{readxl} (Version 1.4.0; Wickham \& Bryan, 2022), \emph{rstatix} (Version 0.7.0; Kassambara, 2021), \emph{rticles} (Version 0.25; Allaire et al., 2023), \emph{stringr} (Version 1.4.0; Wickham, 2019), \emph{tibble} (Version 3.1.6; Müller \& Wickham, 2021), \emph{tidyr} (Version 1.2.0; Wickham \& Girlich, 2022), \emph{tidyverse} (Version 1.3.1; Wickham et al., 2019), \emph{tinylabels} (Version 0.2.3; Barth, 2022), \emph{viridis} (Version 0.6.2; Garnier et al., 2021a, 2021b), \emph{viridisLite} (Version 0.4.1; Garnier et al., 2021b), \emph{xfun} (Version 0.36; Xie, 2022), \emph{xtable} (Version 1.8.4; Dahl, Scott, Roosen, Magnusson, \& Swinton, 2019), \emph{xts} (Version 0.12.1; Ryan \& Ulrich, 2020), and \emph{zoo} (Version 1.8.10; Zeileis \& Grothendieck, 2005) for all our analyses (descriptive statistics, correlations, and multilevel regression). Statistical assumptions including linearity, homogeneity of variance, and normal distribution of residuals were tested and confirmed with RStudio {[}palmeri2020{]}. An alpha level of 0.05 was used for the statistical tests.

@@

Teachers' average heart rate during the entire course of the study was approximately 90.09 bpm with a standard deviation of 15.76 and a range from 51 to 164 bpm.

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-magrittr}{}}%
Bache, S. M., \& Wickham, H. (2022). \emph{Magrittr: A forward-pipe operator for r}. Retrieved from \url{https://CRAN.R-project.org/package=magrittr}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-xtable}{}}%
Dahl, D. B., Scott, D., Roosen, C., Magnusson, A., \& Swinton, J. (2019). \emph{Xtable: Export tables to LaTeX or HTML}. Retrieved from \url{https://CRAN.R-project.org/package=xtable}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-Hmisc}{}}%
Harrell Jr, F. E. (2023). \emph{Hmisc: Harrell miscellaneous}. Retrieved from \url{https://CRAN.R-project.org/package=Hmisc}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-lmerTest}{}}%
Kuznetsova, A., Brockhoff, P. B., \& Christensen, R. H. B. (2017). {lmerTest} package: Tests in linear mixed effects models. \emph{Journal of Statistical Software}, \emph{82}(13), 1--26. \url{https://doi.org/10.18637/jss.v082.i13}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-PerformanceAnalytics}{}}%
Peterson, B. G., \& Carl, P. (2020). \emph{PerformanceAnalytics: Econometric tools for performance and risk analysis}. Retrieved from \url{https://CRAN.R-project.org/package=PerformanceAnalytics}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-xts}{}}%
Ryan, J. A., \& Ulrich, J. M. (2020). \emph{Xts: eXtensible time series}. Retrieved from \url{https://CRAN.R-project.org/package=xts}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-corrplot2021}{}}%
Wei, T., \& Simko, V. (2021). \emph{R package 'corrplot': Visualization of a correlation matrix}. Retrieved from \url{https://github.com/taiyun/corrplot}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-cowplot}{}}%
Wilke, C. O. (2020a). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}

\leavevmode\vadjust pre{\hypertarget{ref-R-gridtext}{}}%
Wilke, C. O. (2020b). \emph{Gridtext: Improved text rendering support for 'grid' graphics}. Retrieved from \url{https://CRAN.R-project.org/package=gridtext}

@@

\leavevmode\vadjust pre{\hypertarget{ref-R-zoo}{}}%
Zeileis, A., \& Grothendieck, G. (2005). Zoo: S3 infrastructure for regular and irregular time series. \emph{Journal of Statistical Software}, \emph{14}(6), 1--27. \url{https://doi.org/10.18637/jss.v014.i06}

### 2024-10-25 02_paper/02_study/01_fitbit_paper/Submission/FitBit_Plots_MK.Rmd

@@

# standardisierte Koeffizienten
zmodell <- lm(scale(mean_hr_std) ~ scale(mean_confi) + scale (mean_disrup) + scale(mean_te), 
              data = df_lm_subset)
summary(zmodell)

>>>>

main <-
  left_join(x = main, y = df_merge,
            by = "ID")

@@

# standardisierte Koeffizienten
zmodell <- lm(scale(mean_hr_std) ~ scale(mean_confi) + scale(mean_disrup) + scale(mean_te), 
              data = df_lm_subset)
summary(zmodell)

### 2024-10-25 02_paper/02_study/02_expertise_paper/expertise_2024_09_26_no_outlierdetection_MK.Rmd

>>>>

#### 2.2.2 Letter search
```{r letter_search, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

##################### LETTER SEARCH ########################

# filter
df_aoi %>%
  filter(TOI == "Letter_search") %>% 
  dplyr::select (
    TOI,
    Group,
    Participant,
    Duration_of_interval) %>% 
  mutate(Duration_of_interval_sec = 
           round(Duration_of_interval/1000, digits = 2)
         ) -> df_letter
# missing IDs: 101, 111, 205

# N, M, SD, min & max 
letter.table <-
  df_letter %>%
  group_by(Group) %>%
  summarise(
    N = n(),
    "M" = round(mean(Duration_of_interval_sec), digits = 2),
    "SD" = round(sd(Duration_of_interval_sec), digits = 2),
    "Min" = round(min(Duration_of_interval_sec), digits = 2),
    "Max" = round(max(Duration_of_interval_sec), digits = 2)
  )

knitr::kable(letter.table,
             caption = "N, M, SD, min & max letter search in seconds")

#### t-test & effect size "Letter search"
```{r letter_ttest, echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

# LETTER SEARCH 
# t-test for expertise differences
t.test(
  x = df_letter$Duration_of_interval_sec[df_letter$Group == "Expert"],
  y = df_letter$Duration_of_interval_sec[df_letter$Group == "Novice"],
  var.equal = TRUE
)

# NUMBER OF FIXATIONS PER MINUTE (micro-teaching unit)
# effect size for expertise differences
d_letter <- CohenD(
  x = df_letter$Duration_of_interval_sec[df_letter$Group == "Expert"],
  y = df_letter$Duration_of_interval_sec[df_letter$Group == "Novice"],
  na.rm = TRUE
)

round(d_letter, 2)
